SDR enhancement by clouds

### 2024-03-17 article/article.tex
Commit 2024-03-16 16:14
Commit 2024-03-17 22:10
Commit 2024-03-17 23:19

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-15}

@@

We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
participates in AERONET, where we operate a Cimel photometer, colocated to
the CM-21 pyranometer, since 2003

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/energy-3}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/energy-2}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/energy-1}

@@

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-12}
\end{figure}

@@

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-17}

@@

We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-7}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-6}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-5}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-8}

\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-12}
\end{figure}

@@

@@

\caption{Distribution of }\label{fig:unnamed-chunk-14}
\end{figure}
